Computer Science House Constitution

### 2016-11-10 articles.tex
Small Aesthetic Changes
i) Chairman, Secretary, Ad Hoc Director is now the order of non-Voting
Executive Board members.
ii) added (s) to Research and Development since there can be two
directors for the position.
Appeal of an Executive Board decision
Members can take a petition to house meeting and can have a vote there to appeal an executive board decision.

% ARTICLE IV - EXECUTIVE BOARD
\article{Executive Board}
The Executive Board is the main governing body of the House.
Its purpose is to provide leadership and direction for the House, to oversee the day-to-day operations of the House, and to initiate and organize programs and projects for the House.
It is composed of the seven permanent directors and the Chairman.
\\*\\*
There is one permanent directorship for each major aspect of the government of the House and each one is chaired by an Executive Board member.
Ad-hoc directorships are created on an as-needed basis.
They are generally very task oriented and are chaired by a House member.
A directorship has some jurisdiction in its area of interest and often is responsible for the day-to-day decisions regarding its area of interest.
Any large expenditures or large effect decisions must be brought before the entire House
\asection{Members of the Executive Board}
\asubsection{Voting Members}
\begin{itemize}
	\item Evaluations Director
	\item Social Director(s)
	\item Financial Director
	\item Research and Development Director
	\item House Improvements Director
	\item Operational Communications Director
	\item House History Director
\end{itemize}
\asubsection{Non-Voting Members}
\begin{itemize}
	\item Ad Hoc Directors
        \item House Secretary
        \item Chairman
\end{itemize}
\asection{Closed Executive Board}
Closed Executive Board Meetings are open only to the Chairman, Voting Members of the Executive Board, and those with the express permission of the Executive Board.
A closed Executive Board meeting may be called at any time by any member of the Executive Board.
However, the Chairman and at least two-thirds of the Voting Members must be present for the meeting to be called.

@@

\asection{Appeals}
Decisions made by the Executive Board may be appealed and overturned.
To initiate an appeal, a member must have the support of three voting members of the Executive Board, or a petition with the signatures of one-third of Active Members.
After the appeal is presented, a Simple Majority vote is held by the Executive Board whether or not to overturn and reevaluate the decision.
If the vote passes, the Executive Board may discuss and make a new ruling by another Simple Majority vote.

>>>>

% ARTICLE IV - EXECUTIVE BOARD
\article{Executive Board}
The Executive Board is the main governing body of the House.
Its purpose is to provide leadership and direction for the House, to oversee the day-to-day operations of the House, and to initiate and organize programs and projects for the House.
It is composed of the seven permanent directors and the Chairman.
\\*\\*
There is one permanent directorship for each major aspect of the government of the House and each one is chaired by an Executive Board member.
Ad-hoc directorships are created on an as-needed basis.
They are generally very task oriented and are chaired by a House member.
A directorship has some jurisdiction in its area of interest and often is responsible for the day-to-day decisions regarding its area of interest.
Any large expenditures or large effect decisions must be brought before the entire House
\asection{Members of the Executive Board}
\asubsection{Voting Members}
\begin{itemize}
	\item Evaluations Director
	\item Social Director(s)
	\item Financial Director
	\item Research and Development Director(s)
	\item House Improvements Director
	\item Operational Communications Director
	\item House History Director
\end{itemize}
\asubsection{Non-Voting Members}
\begin{itemize}
	\item Chairman 
        \item House Secretary
        \item Ad Hoc Director
\end{itemize}
\asection{Closed Executive Board}
Closed Executive Board Meetings are open only to the Chairman, Voting Members of the Executive Board, and those with the express permission of the Executive Board.
A closed Executive Board meeting may be called at any time by any member of the Executive Board.
However, the Chairman and at least two-thirds of the Voting Members must be present for the meeting to be called.

@@

\asection{Appeals}
\asubsection{Executive Board Appeal}
Decisions made by the Executive Board may be appealed and overturned.
To initiate an appeal, a member must have the support of three voting members of the Executive Board, or a petition with the signatures of one-third of Active Members.
After the appeal is presented, a Simple Majority vote is held by the Executive Board whether or not to overturn and reevaluate the decision.
If the vote passes, the Executive Board may discuss and make a new ruling by another Simple Majority vote.
\asubsection{House Appeal} 
To initiate an appeal to House of an Executive Board decision, a petition with the signatures of two-thirds of Active Members must be brought to a House Meeting. After the appeal is presented and discussed, a Two-Thirds vote is held by the attending members. 
If the vote passes, attending members may discuss and make a new ruling by a Two-Thirds vote.
